Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-16 ieee_paper.tex
moving heat map in section 3
fixing caption of heat maps

In the special case $n_v=n_m=1$ in single precision
$$I_b = \frac{1}{4} \frac{ n_z }{ n_z + 1} \approx \frac{1}{4}$$
%$$I_w = \frac{n_z }{2  + 36  n_z} \approx \frac{1}{36}$$
$$I_w = \frac{n_z }{2  + (4+cl/2)  n_z} \approx \frac{1}{4+cl/2}$$

In the special case $n_v=n_m=4$ in single precision
$$I_b = \frac{32 n_z }{ n_z 20 + 80} \approx \frac{32}{20} = \frac{8}{5} $$
%$$I_w = \frac{32 n_z }{64 + n_z 84} \approx \frac{32}{84} = \frac{8}{21} $$
$$I_w = \frac{32 n_z }{64 + (20+cl) n_z} \approx \frac{32}{84} = \frac{8}{21} $$
The above formulas have been applied to MIC, which has a cache size $cl=64$ bytes.

@@

@@

\begin{figure*}
\centering
\subfigure[Best case.]{\includegraphics[width=.33\linewidth]{figures/flops_to_bytes_best-crop.pdf}} %\label{fig:ratio_best}}
\subfigure[Worst case.]{\includegraphics[width=.33\linewidth]{figures/flops_to_bytes_worst-crop.pdf}}%\label{fig:ratio_worst}}
\subfigure[Worst case (No cacheline effects)]{\includegraphics[width=.33\linewidth]{figures/flops_to_bytes_no_cache-crop.pdf}}%\label{fig:ratio_nocache}}
\caption{Ratio of flops to bytes; (a) simple count of flops and bytes that require transfer from memory;(b) best and (c) worst
case taking into account that bringing one element of $x$ into memory brings along the remainder of the cache line.}
\label{fig:ratio_bytes_flops}
\end{figure*}

>>>>

%% In the special case $n_v=n_m=1$ in single precision
%% $$I_b = \frac{1}{4} \frac{ n_z }{ n_z + 1} \approx \frac{1}{4}$$
%% %$$I_w = \frac{n_z }{2  + 36  n_z} \approx \frac{1}{36}$$
%% $$I_w = \frac{n_z }{2  + (4+cl/2)  n_z} \approx \frac{1}{4+cl/2}$$

%% In the special case $n_v=n_m=4$ in single precision
%% $$I_b = \frac{32 n_z }{ n_z 20 + 80} \approx \frac{32}{20} = \frac{8}{5} $$
%% %$$I_w = \frac{32 n_z }{64 + n_z 84} \approx \frac{32}{84} = \frac{8}{21} $$
%% $$I_w = \frac{32 n_z }{64 + (20+cl) n_z} \approx \frac{32}{84} = \frac{8}{21} $$
%% The above formulas have been applied to MIC, which has a cache size $cl=64$ bytes.

@@

Figure~\ref{fig:ratio_bytes_flops} presents the flop to byte ratios in
the best and the worst case.

\begin{figure*}
  \centering
  \subfigure[Best case.]{\includegraphics[width=.33\linewidth]{figures/flops_to_bytes_best-crop.pdf}\label{fig:ratio_best}}%
  \subfigure[Worst case.]{\includegraphics[width=.33\linewidth]{figures/flops_to_bytes_worst-crop.pdf}\label{fig:ratio_worst}}%
  \subfigure[Worst case (No cacheline effects)]{\includegraphics[width=.33\linewidth]{figures/flops_to_bytes_no_cache-crop.pdf}\label{fig:ratio_worst_nocache}}

  \caption{Ratio of flops to bytes: in the best case in
    \ref{fig:ratio_best} best; in the worst case when $cl=64$ in
    \ref{fig:ratio_worst}; and in the worst case neglecting that the
    memory transfers are by batch of size $cl$ in
    \ref{fig:ratio_worst_nocache}}
  \label{fig:ratio_bytes_flops}
\end{figure*}

@@
